An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-07 uai2017/paper.tex
added another reference, probably our last one, I hope

\textbf{We benchmark with the ADAGrad~\citep{adagrad} implementation of Sparse
Matrix Factorization described in~\citep{Canny:2013:BDA:2487575.2487677}.
(Daniel: is this the correct citation for BIDMach? I assume this is what we will
use)}

>>>>

\textbf{We benchmark with the ADAGrad~\citep{adagrad} implementation of Sparse
Matrix Factorization described in~\citep{Canny:2013:BDA:2487575.2487677}, which
is a variant of Alternating Least Squares~\citep{Koren:2009:MFT:1608565.1608614}.
(Daniel: is this the correct citation for BIDMach? I assume this is what we will
use)}
